sensiAnPaper1All

### 2016-03-23 sensiAnPaper1All.Rmd
add an unequal option for looking at 'old' insecticide scenarios

  nScenarios <- 3  
  #nScenarios <- 100
  #nScenarios <- 1000  
  #nScenarios <- 10000

@@

  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment )

  ## save results objects as rda for re-use
  #save(listOutMix, file=paste0(outFolder,'listOutMix.rda'))
  #save(listOutI1, file=paste0(outFolder,'listOutI1.rda'))
  #save(listOutI2, file=paste0(outFolder,'listOutI2.rda'))

  save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

#   save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_3.rda'))
#   save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_3.rda'))
#   save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_3.rda'))

>>>>

  #nScenarios <- 10  
  #nScenarios <- 100
  nScenarios <- 500  
  #nScenarios <- 10000

@@

  ## do model runs
  # listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment )
  # listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment )
  # listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment )

  ## 23/3/16 expt with an 'old' insecticide
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment, old_insecticide=TRUE )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment, old_insecticide=TRUE )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment, old_insecticide=TRUE )

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix_unequal.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_unequal.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_unequal.rda'))

  # save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  # save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  # save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_10000.rda'))
